---
title: "entity"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  md_document:
    toc: true      
---

```{r, echo=FALSE}
desc <- suppressWarnings(readLines("DESCRIPTION"))
regex <- "(^Version:\\s+)(\\d+\\.\\d+\\.\\d+)"
loc <- grep(regex, desc)
ver <- gsub(regex, "\\2", desc[loc])
verbadge <- sprintf('<a href="https://img.shields.io/badge/Version-%s-orange.svg"><img src="https://img.shields.io/badge/Version-%s-orange.svg" alt="Version"/></a></p>', ver, ver)
````

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/0.1.0/active.svg)](http://www.repostatus.org/#active)
[![Build Status](https://travis-ci.org/trinker/entity.svg?branch=master)](https://travis-ci.org/trinker/entity)
[![Coverage Status](https://coveralls.io/repos/trinker/entity/badge.svg?branch=master)](https://coveralls.io/r/trinker/entity?branch=master)
`r verbadge`

```{r, echo=FALSE, message=FALSE}
library(knitr)
knit_hooks$set(htmlcap = function(before, options, envir) {
  if(!before) {
    paste('<p class="caption"><b><em>',options$htmlcap,"</em></b></p>",sep="")
    }
    })
knitr::opts_knit$set(self.contained = TRUE, cache = FALSE)
knitr::opts_chunk$set(fig.path = "inst/figure/")
```

**entity** is wrapper to simplify and extend [**NLP**](https://cran.r-project.org/web/packages/NLP/index.html) and [**openNLP**](https://cran.r-project.org/web/packages/openNLP/index.html) named entity recognition.  The package contains 6 entity extractors that take a text vector and return a lest of vectors of named entities.  The entity extractors include:

1. `person_entity`
2. `location_entity`
3. `organization_entity`
4. `date_entity`
5. `money_entity`
6. `percent_entity`
        
# Installation

To download the development version of **entity**:

Download the [zip ball](https://github.com/trinker/entity/zipball/master) or [tar ball](https://github.com/trinker/entity/tarball/master), decompress and run `R CMD INSTALL` on it, or use the **pacman** package to install the development version:

```r
if (!require("pacman")) install.packages("pacman")
pacman::p_load_gh("trinker/entity")
```

# Contact

You are welcome to:
* submit suggestions and bug-reports at: <https://github.com/trinker/entity/issues>
* send a pull request on: <https://github.com/trinker/entity/>
* compose a friendly e-mail to: <tyler.rinker@gmail.com>

# Examples

The following examples demonstrate some of the functionality of **termco**.

## Load the Package/Data

```{r, message=FALSE}
library(entity)
```

I will demonstrate the 6 annotators on this [Wikipedia excerpt](https://en.wikipedia.org/wiki/Bell_Labs) about Bell Labs.

```{r}
wiki <- c("Bell Laboratories (also known as Bell Labs and formerly known as AT&T Bell Laboratories and Bell Telephone Laboratories) is a research and scientific development company that belongs to Alcatel-Lucent.", 
    "Its headquarters are located in Murray Hill, New Jersey, in addition to other laboratories around the rest of the United States and in other countries.", 
    "The historic laboratory originated in the late 19th century as the Volta Laboratory and Bureau created by Alexander Graham Bell.", 
    "Bell Labs was also at one time a division of the American Telephone & Telegraph Company (AT&T Corporation), half-owned through its Western Electric manufacturing subsidiary.", 
    "Researchers working at Bell Labs are credited with the development of radio astronomy, the transistor, the laser, the charge-coupled device (CCD), information theory, the UNIX operating system, the C programming language, S programming language and the C++ programming language.", 
    "Eight Nobel Prizes have been awarded for work completed at Bell Laboratories.",
    "And an extray line not from wiki worth 2 cents or .001% of 1 percent."
)
```

## Entity Extractors

### Person Entities

```{r}
person_entity(wiki)
```

### Location Entities

```{r}
location_entity(wiki)
```

### Organization Entities

```{r}
organization_entity(wiki)
```

### Entities

```{r}
date_entity(wiki)
```

### Money Entities

```{r}
money_entity(wiki)
```

### Percent Entities

```{r}
percent_entity(wiki)
```


## Plotting

```{r, fig.height = 8}
organizations <- organization_entity(presidential_debates_2012$dialogue)
plot(organizations)
```
